\documentclass{amsart}
\usepackage[shortlabels]{enumitem}
\title{}
\author{}
\address{}
\email{}
\begin{document}
\begin{abstract}
  some small abstract with a \dots footnote?\footnote{this shouldn't be a problem I don't think}
\end{abstract}

\maketitle

some text in the document, not in the abstract\dots\footnote[1234567890]{This footnote was not originally in the text, but is added just here for \emph{testing purposes}. Well this is no longer true since I put this here in this dedicated document for testing footnotes. Yes, I know, very interesting. Can we put display math in a footnote?

        Or paragraphs?

        Let's find out:
        \[
        \sum\prod^n_{i = 0} \alpha_i .
        \]
        I think we'll get our answer from this.

        Oh wow, yeah we can put pretty much anything in here, huh.
        \begin{enumerate}[(i)]
        \item here's one
        \item and another
        \item and the last
        \end{enumerate}

        You can't put a figure, can you?

        No, thankfully you cannot put a figure. But now let's see what happens when we put ... a lot of text in here.

        This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.         This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.        This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.        This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.        This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.        This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.        This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.        This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.        This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.        This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.        This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.        This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.        This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.        This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.        This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.  This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.  This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.  This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.  This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.  This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.  This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.  This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.  This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.  This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.  This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.  This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.  This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.  This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere.  This is a story that goes no where. Just when you think that it might, or really, to be more accurate, well before you think it might go anywhere at all, you end up right back where you started: Nowhere. 

        Can we reference this figure? Figure I would be ... pretty shocked.}
\end{document}
